---
title: "Getting Started"
author: "<h4>Authors: <i>`r auths <- eval(parse(text = gsub('person','c',read.dcf('../DESCRIPTION', fields = 'Authors@R'))));paste(auths[names(auths)=='given'],auths[names(auths)=='family'], collapse = ', ')`</i></h4>"
date: "<h4>Vignette updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{downloadR}
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(downloadR)
```

# Introduction

`downloadR` is an echoverse module that provides single- and multi-threaded
downloading functions for R. It wraps several download backends including
[axel](https://github.com/axel-download-accelerator/axel) (multi-threaded),
`wget`, and R's built-in `download.file`. It also provides convenience
functions for working with AWS S3, Figshare, and Zenodo repositories.

# Download files

## Multi-threaded

The core function `downloader()` supports a variety of download backends.
For multi-threaded downloads of a single file, use the `axel` method.

```{r multi-threaded, eval = curl::has_internet()}
input_url <- paste(
    "https://github.com/RajLabMSSM/Fine_Mapping",
    "raw/master/Data/lead.SNP.coords.csv", sep = "/")
out_path <- downloadR::downloader(input_url = input_url,
                                  download_method = "download.file",
                                  nThread = 1)
csv <- utils::read.csv(out_path)
knitr::kable(head(csv))
```

## Single-threaded

For single-threaded downloads, you can use `wget` or `download.file`.

```{r single-threaded, eval = curl::has_internet()}
out_path2 <- downloadR::downloader(input_url = input_url,
                                   download_method = "download.file",
                                   force_overwrite = TRUE)
```

# Download VCF

`download_vcf()` is a specialised function for downloading Variant Call Format
(VCF) files. It automatically attempts to download both the VCF and its
tabix index file (`.tbi`), if available.

```{r download-vcf, eval = FALSE}
vcf_url <- "https://gwas.mrcieu.ac.uk/files/ieu-a-298/ieu-a-298.vcf.gz"
out_paths <- downloadR::download_vcf(vcf_url = vcf_url)
```

# Load R data

`load_rdata()` is a convenience function that can read `.rda`, `.rdata`,
or `.rds` files from either a local or remote path. Remote files are
downloaded automatically before loading.

```{r load-rdata, eval = curl::has_internet()}
fileName <- paste0(
    "https://github.com/RajLabMSSM/",
    "Fine_Mapping_Shiny/raw/master/www/BST1.finemap_DT.RDS")
dat <- downloadR::load_rdata(fileName)
knitr::kable(head(dat, 3))
```

# AWS S3

The `aws()` function downloads files from Amazon S3 buckets using the
`aws.s3` package.

```{r aws, eval = FALSE}
bucket <- "s3://broad-alkesgroup-ukbb-ld/"
input_url <- "UKBB_LD/chr10_135000001_138000001.gz"
out <- downloadR::aws(input_url = input_url, bucket = bucket)
```

# Figshare

## List files

`figshare_list()` queries the Figshare API to list all downloadable files
in a repository.

```{r figshare-list, eval = curl::has_internet()}
files <- downloadR::figshare_list(id = "14703003")
knitr::kable(files[, c("name", "size")])
```

## Download files

`figshare_download()` combines listing and downloading into one step.

```{r figshare-download, eval = FALSE}
files <- downloadR::figshare_download(
    id = "14703003",
    suffix = "Earthworm_sFig1_cluster_marker.xlsx")
```

# Zenodo

## List files

`zenodo_list()` retrieves metadata for all files in a Zenodo record.
Requires a Zenodo personal access token (set via the `zenodo_token`
environment variable or passed directly).

```{r zenodo-list, eval = FALSE}
zen_dat <- downloadR::zenodo_list(
    token = "<your-token>",
    concept_doi = "10.5281/zenodo.7062237")
```

## Upload files

`zenodo_upload()` creates a new Zenodo record, uploads files, and publishes.

```{r zenodo-upload, eval = FALSE}
files <- sapply(seq_len(3), function(i) {
    tmp <- tempfile(fileext = ".txt")
    writeLines(letters, tmp)
    return(tmp)
})
zout <- downloadR::zenodo_upload(
    files = files,
    title = "test_repo")
```

# Session Info

<details>

```{r Session Info}
utils::sessionInfo()
```

</details>

<br>
